KIN: A method to infer relatedness from low-coverage ancient DNA

### 2022-05-16 paper_overleaf/KIN_a_method_to_estimate_relatedness_from_low_coverage_data_supplements.tex

\begin{figure}[!ht]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot1.png}
    \caption{Plots showing proportion of differences in windows along the genome for some of the pairs of relatives for which KIN differs from READ. (A) AITI62B-OTTM156 (READ estimates Identical individuals, lcMLkin does not have sufficient data, and KIN predicts parent-child. (B) UNTA5867-UNTA5868Sk1 (READ estimates Second Degree, lcMLkin does not have sufficient data, and KIN predicts parent-child). (C) AITI40-AITI72 (READ estimates Unrelated individuals, lcMLkin shows 3rd-5th degree, and KIN predicts 3rd degree.)
    (D) AITI2-AITI55 (READ estimates Unrelated individuals, lcMLkin and KIN predicts predict second degree.)}
    \label{figS8:eg1}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot2.png}
    \caption{Plots showing proportion of differences in windows along the genome for the first degree relatives for which KIN differs from lcMLkin. We expect to see proportion of difference to be close to $p_0$ in $25\%$ windows, $p_1$ in $50\%$ windows, and $p_2$ in $25\%$ windows. For parent-child, we expect the proportion of differences to stay close to $p_1$ with some noise. (A) AITI43-AITI55 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child. (B) AITI70-AITI72 (READ estimates first degree, lcMLkin predicts parent-child, while KIN predicts siblings. (C) OBKR76-POST99 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child.}
    \label{figS9:eg2}
\end{figure}

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot1.png}
    \caption{Plots showing proportion of differences in windows along the genome for some pairs of relatives for which there is contradiction among KIN, READ and lcMLkin. (A) shows a case for which KIN and lcMLkin together disagree with READ, and (B) shows a case where KIN and lcMLkin differ, while READ does not have enough power. (C) and (D) show the two pairs for which all three methods disagree. We expect to see proportion of differences for second degree to be close to $p_0$ in $50\%$ windows, and $p_1$ in $50\%$ windows. For third degree we expect $75\%$ windows to be close to $p_0$, and $25\%$ windows to be close to $p_1$. For unrelated, we expect the proportion of differences to stay close to $p_0$ with some noise. (A) AITI95-AITI98 (READ estimates unrelated, lcMLkin and KIN predict second degree. (B) AITI72-AITI77A (READ estimates unrelated (READ does not distinguish between unrelated and third degree), lcMLkin shows unrelated, and KIN predicts third degree). (C) POST131-POST28 (READ estimates Unrelated, lcMLkin shows 3rd-5th degree, and KIN predicts second degree.) (D) ALT3-ALT4 (READ estimates unrelated, lcMLkin shows second degree and KIN predicts third degree.)}
    \label{figS8:eg1}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=18cm]{supplementary_info/plots/egplot2.png}
    \caption{Plots showing proportion of differences in windows along the genome for the first degree relatives for which KIN differs from lcMLkin. We expect to see proportion of differences for siblings to be close to $p_0$ in $25\%$ windows, $p_1$ in $50\%$ windows, and $p_2$ in $25\%$ windows. For parent-child, we expect the proportion of differences to stay close to $p_1$ with some noise. (A) AITI43-AITI55 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child. (B) AITI70-AITI72 (READ estimates first degree, lcMLkin predicts parent-child, while KIN predicts siblings. (C) OBKR76-POST99 (READ estimates first degree, lcMLkin predicts siblings, while KIN predicts parent-child.}
    \label{figS9:eg2}
\end{figure}
